---
title: "Homework2"
author: "Yining Song"
output: pdf_document
---

Problem3

Version control can show the details of improvements or differences between versions. Therefore, it can record our progress in the classroom in a step by step manner, which will help us get a better understanding of the materials we need to learn, as well as inspire us of what needs improvements.


Problem 4

(a)
```{r}
data1=read.csv("Sensory.dat.txt")
summary(data1)
```
Obviously the data were messed up, and the title did not match the data. So we skip the title line:

```{r}
data1=read.table("Sensory.dat.txt",fill = T,skip = 2)
print(data1)
```
We do not need the indicators 1 to 10, so we remove them from data:

```{r}
data1[1,]=data1[1,][-1]
data1[4,]=data1[4,][-1]
data1[7,]=data1[7,][-1]
data1[10,]=data1[10,][-1]
data1[13,]=data1[13,][-1]
data1[16,]=data1[16,][-1]
data1[19,]=data1[19,][-1]
data1[22,]=data1[22,][-1]
data1[25,]=data1[25,][-1]
data1[28,]=data1[28,][-1]
data1=data1[,-6]
names(data1)=c('1','2','3','4','5')
tidydata1=data1
print(tidydata1)
```
This is the tidy dataset.

```{r}
summary(tidydata1)
```


(b)
```{r}
data2=read.csv("LongJumpData.dat.txt")
summary(data2)
```
Obviously there are missing values in the table, and the title did not match the data. So we fill out the missing values and skip the title line:

```{r}
data2=read.table("LongJumpData.dat.txt",fill = T,skip = 1)
print(data2)
```

Now we summary the years and the performances in two columns:
```{r}
Year=c(data2[,1],data2[,3],data2[,5],data2[,7])
Performance=c(data2[,2],data2[,4],data2[,6],data2[,8])
tidydata2=cbind(Year,Performance)[-c(23,24),]
tidydata2[,1]=tidydata2[,1]+1900
print(tidydata2)
```
This is the tidy dataset.

```{r}
summary(tidydata2)
```

(c)
```{r}
data3=read.csv("BrainandBodyWeight.dat.txt")
print(data3)
```
Obviously there are missing values in the table, and the title did not match the data. So we fill out the missing values and skip the title line:

```{r}
data3=read.table("BrainandBodyWeight.dat.txt",fill = T,skip = 1)
print(data3)
```

Now we summary the body weights and the brain weights in two columns:
```{r}
BodyW=c(data3[,1],data3[,3],data3[,5])
BrainW=c(data3[,2],data3[,4],data3[,6])
tidydata3=cbind(BrainW,BodyW)[-63,]
print(tidydata3)
```
This is the tidy dataset.

```{r}
summary(tidydata3)
```


(d)
By viewing the data in the txt file, we can see that we have data in 6 treatment levels, each have 3 data points. So we first store them in 6 vectors manually.
```{r}
Ife1=c(16.1,15.3,17.5)
Ife2=c(16.6,19.2,18.5)
Ife3=c(20.8,18.0,21.0)
PED1=c(8.1,8.6,10.1)
PED2=c(12.7,13.7,11.5)
PED3=c(14.4,15.4,13.7)
Yield=c(Ife1,Ife2,Ife3,PED1,PED2,PED3)
treatments=c(rep(1,3),rep(2,3),rep(3,3),rep(4,3),rep(5,3),rep(6,3))
tidydata4=cbind(Yield,treatments)
print(tidydata4)
```



Problem 5

```{r}
library(swirl)
.datapath <- file.path(path.package('swirl'), 'Courses',
                       'R_Programming_E', 'Looking_at_Data',
                       'plant-data.txt')
plants <- read.csv(.datapath, strip.white=TRUE, na.strings="")
.cols2rm <- c('Accepted.Symbol', 'Synonym.Symbol')
plants <- plants[, !(names(plants) %in% .cols2rm)]
names(plants) <- c('Scientific_Name', 'Duration', 'Active_Growth_Period',
                   'Foliage_Color', 'pH_Min', 'pH_Max',
                   'Precip_Min', 'Precip_Max',
                   'Shade_Tolerance', 'Temp_Min_F')
```

